Application of Turchin's method of statistical regularization

### 2018-03-02 AYSS-2017/article/ayss2017-Zeleniy.tex
Resize to 5 page

\subsection{Strategy}\label{sec:theory:strat}

Consider eq.~\ref{eq-01} in operator form:
\begin{equation}
	\label{eq-02}
    \hat{K}\varphi = f.
\end{equation}

According to statistical decision theory (\cite{james2006statistical}), one can define a reconstruction strategy  $\hat{\varphi} = \hat{S}[f]$, which uses a prior information. Good strategy minimize an impact of prior information (which could be wrong). That could be achieved by introducing the loss-function:
\begin{equation*}
	L(\varphi,\hat{S}[f]) = ||\varphi-\hat{S}[f])||_{L_2},
\end{equation*}

For this loss-function:
\begin{equation}
	\label{eq:opt}
	\hat{S}[f] = E[\varphi|f] = \int \varphi P(\varphi|f)d\varphi
\end{equation}

Strategy depend on a prior information $P(\varphi)$:
\begin{equation*}
	P(\varphi|f)= \frac{P(\varphi)P(f|\varphi)}{\int d\varphi P(\varphi)P(f|\varphi)} 
\end{equation*}

Errors of solution:
\begin{equation*}
	D(x_1,x_2)  = E[\varphi(x_1) - \hat{S}[f](x_1)][\varphi(x_2) - \hat{S}[f](x_2)]
\end{equation*}
Let us consider what a prior information can we use?

@@

The resulting prior probability density for the Gaussian random process:
\begin{equation}
	P_{\alpha}(\vec{\varphi})  = \frac{\alpha^{Rg(\Omega)/2}\det\Omega^{1/2}}{(2\pi)^{N/2}} 
    \exp\left(-\frac{1}{2}(\vec{\varphi},\alpha\Omega\vec{\varphi})\right),
\end{equation}
where  $\alpha = \alpha(\omega)$ - parameter of smoothness.
The prior information depends on $\alpha$-smoothness parameter. This parameter could be estimated in a few different ways:
\begin{enumerate}
\item Select manually using known smoothness. This is rare probability.
\item Use most probable parameter: $\alpha^* = \max P(\alpha|f).$
\item Use a prior information about smoothness: 
  \begin{equation}\label{eq:varAposteriorAlpha}
      P(\varphi)  = \int P_{\alpha}(\varphi) P(\alpha)~d\alpha
  \end{equation}
\item Use a posterior information about smoothness: 
  \begin{equation}\label{eq:solveAposteriorAlpha}
      \hat{S}[f] = \int d\alpha \hat{S}_{\alpha}[f] P(\alpha|f),
  \end{equation} 
\end{enumerate}

In fact, methods 3 and 4 are equivalent.

>>>>

\subsection{Strategy}\label{sec:theory:strat}
Consider eq.~\ref{eq-01} in operator form:
\begin{equation}
	\label{eq-02}
    \hat{K}\varphi = f.
\end{equation}
According to statistical decision theory (\cite{james2006statistical}), one can define a reconstruction strategy  $\hat{\varphi} = \hat{S}[f]$, which uses a prior information. Good strategy minimize an impact of prior information (which could be wrong). That could be achieved by introducing the loss-function:
\begin{equation*}
	L(\varphi,\hat{S}[f]) = ||\varphi-\hat{S}[f])||_{L_2},
\end{equation*}
For this loss-function:
\begin{equation}
	\label{eq:opt}
	\hat{S}[f] = E[\varphi|f] = \int \varphi P(\varphi|f)d\varphi
\end{equation}
Strategy depend on a prior information $P(\varphi)$:
\begin{equation*}
	P(\varphi|f)= \frac{P(\varphi)P(f|\varphi)}{\int d\varphi P(\varphi)P(f|\varphi)} 
\end{equation*}
Errors of solution:
\begin{equation*}
	D(x_1,x_2)  = E[\varphi(x_1) - \hat{S}[f](x_1)][\varphi(x_2) - \hat{S}[f](x_2)]
\end{equation*}
Let us consider what a prior information can we use?

@@

The resulting prior probability density for the Gaussian random process:
\begin{equation}
	P_{\alpha}(\vec{\varphi})  = \frac{\alpha^{Rg(\Omega)/2}\det\Omega^{1/2}}{(2\pi)^{N/2}} 
    \exp\left(-\frac{1}{2}(\vec{\varphi},\alpha\Omega\vec{\varphi})\right),
\end{equation}
where  $\alpha = \alpha(\omega)$ - parameter of smoothness.
The prior information depends on $\alpha$-smoothness parameter. This parameter could be estimated in a few different ways: \\
\indent a) select manually using known smoothness, but this is rare probability; \\
\indent b) use most probable parameter: $\alpha^* = \max P(\alpha|f);$ \\
\indent c) use a prior information about smoothness: 
  \begin{equation}\label{eq:varAposteriorAlpha}
      P(\varphi)  = \int P_{\alpha}(\varphi) P(\alpha)~d\alpha ;
  \end{equation}
\indent d) use a posterior information about smoothness: 
  \begin{equation}\label{eq:solveAposteriorAlpha}
      \hat{S}[f] = \int d\alpha \hat{S}_{\alpha}[f] P(\alpha|f).
  \end{equation} 
In fact, methods (c) and (d) are equivalent.
